\def\letterbody{
  I am writing in support of the promotion of Claire Le~Goues to the position of
  Associate Professor with indefinite tenure. Claire is currently my
  Ph.D. co-advisor, and she is largely responsible for my success as a student.

  I have known Claire for eleven years, since she was a graduate student at the
  University of Virginia. I met her through a mutual friend who was a member of
  the same research group as her. Although I wasn't close friends with Claire, I
  was fascinated by her research on GenProg. My interest in the GenProg project
  was one of the major factors that kindled my initial interest in computer
  science and motivated my decision to return to school and pursue a Ph.D.

  I would not be a student at Carnegie Mellon University if it were not for
  Claire. In 2016, near the end of my undergraduate education at the University
  of Virginia, I was working on research as a member of Claire's Ph.D.\
  advisor's group. As my graduate school application deadline was approaching,
  Claire visited the group office at UVa to meet with colleagues. When she saw
  me she bluntly asked me if I was applying to CMU: I was not. I was convinced
  that applying would have been a waste of time and money because of my
  self-perceived weak academic history and fear of the strong competition at top
  schools. Claire informed me that I was wrong and insisted that I apply,
  encouraging me to email her directly if I had any questions or needed any help
  (which I did). If she had not taken the time to initiate this conversation I
  would literally not be where I am today.

  I took 17-355/17-665/17-819, Program Analysis with Claire in the Spring of
  2018 and was a TA for the same class in the Spring of 2020, so I have had time
  to observe Claire's teaching style. I really enjoy her classes: she genuinely
  loves her field and always teaches with great enthusiasm. The discussions in
  class were engaging, and the assignments were interesting and they always
  helped with my understanding of the course material. While I was a TA, she was
  very receptive to my ideas for ways to improve the course and even allowed me
  to design and implement my own assignments. My interactions with her in the
  classroom and observations of her interaction with REU students have shown me
  that she cares deeply about pedagogy.

  Claire has been an extremely effective co-advisor. Despite the large size of
  her research group, she still is able to find the time to interact with her
  students one-on-one whenever they need guidance. She is skilled at finding the
  right balance between pushing me to my full potential and helping me to set
  realistic goals, and I have exceeded my own expectations for graduate
  school. I have been considering becoming a computer science professor myself,
  and she has made sure that I have opportunities to gain experience with parts
  of the job that aren't usually taught in graduate school. For example, she let
  me write a large part of an NSF Small grant application, and guided me through
  how the process works from start to finish.

  Finally, Claire is fun and enjoyable to spend time with. I am always glad when
  she is able to show up to informal meetings. Graduate school can be a
  stressful, high-pressure environment and having a co-advisor who is cognizant
  of this fact and careful not to add to the stress is invaluable. I look
  forward to finishing my Ph.D. with Claire's guidance, and strongly support her
  promotion.
}
